### 2022-05-11 paper/localpsf.tex
fix typos, minor wordsmithing, in low rank update appendix

In all three cases, direct calculation shows that we have $\mathbf{P}^{(k)}\mathbf{Y}=\mathbf{X}$ after the update, which implies $\left(\mathbf{P}^{(k)}\right)^{-1} \mathbf{X} = \mathbf{B}^{(k)}\mathbf{X}$. Formulas \eqref{eq:res_update} and \eqref{eq:srk_update} perform rank-$k$ updates of $\mathbf{P}^{(k)}$, while formula \eqref{eq:dfp_update} performs a rank-$2k$ update. Formula \eqref{eq:res_update} does not preserve symmetry, and should therefore be used when $\mathbf{B}^{(k)}$ is not symmetric. Formula \eqref{eq:srk_update} preserves symmetry but not positive definiteness, and should therefore be used when $\mathbf{B}^{(k)}$ is symmetric and indefinite. Formula \eqref{eq:dfp_update} preserves both symmetry and positive definiteness, and should therefore be used when $\mathbf{B}^{(k)}$ is symmetric positive definite. Formula \eqref{eq:srk_update} is known as the ``symmetric rank-$k$'' update formula. Formula \eqref{eq:dfp_update} is known as the DFP update formula, named after it's inventor Davidson, and polularizers Fletcher and Powell. For more details on these update formulas, we recommend the discussion in Chapter 6 of \cite{NocedalWright99}. In \cite{NocedalWright99}, one-vector versions of formulas \eqref{eq:srk_update} and \eqref{eq:dfp_update} are discussed thoroughly; the versions here are straightforward generalizations to many-vector updates.

>>>>

In all three cases, direct calculation shows that we have $\mathbf{P}^{(k+1)}\mathbf{Y}=\mathbf{X}$, which implies $\left(\mathbf{P}^{(k+1)}\right)^{-1} \mathbf{X} = \mathbf{B}^{(k)}\mathbf{X}$. Formulas \eqref{eq:res_update} and \eqref{eq:srk_update} perform rank-$m$ updates, while formula \eqref{eq:dfp_update} performs a rank-$2m$ update. Formula \eqref{eq:res_update} does not preserve symmetry, and should therefore be used when $\mathbf{B}^{(k)}$ is not symmetric. Formula \eqref{eq:srk_update} preserves symmetry but not positive definiteness, and should therefore be used when $\mathbf{B}^{(k)}$ is symmetric and indefinite. Formula \eqref{eq:dfp_update} preserves both symmetry and positive definiteness, and should therefore be used when $\mathbf{B}^{(k)}$ is symmetric positive definite. Formula \eqref{eq:srk_update} is known as the ``symmetric rank-$m$'' update formula. Formula \eqref{eq:dfp_update} is known as the DFP update formula, named after it's inventor Davidson, and polularizers Fletcher and Powell. For more details on these update formulas, we recommend the discussion in Chapter 6 of \cite{NocedalWright99}. In \cite{NocedalWright99}, one-vector versions of formulas \eqref{eq:srk_update} and \eqref{eq:dfp_update} are discussed thoroughly; the versions here are straightforward generalizations to many-vector updates.
